---
title : "Bellabeat Case Study"


output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Inroduction** 

 **Bellabeat** is a high-tech manufacturer of health-focused products for women, and meet different team members. **Bellabeat** is a successful small company, but they have the potential to become a larger player in the global [smart device](https://en.wikipedia.org/wiki/Smart_device) market. Urška Sršen, cofounder and Chief Creative Officer of Bellabeat, believes that analyzing smart device fitness data could help unlock new growth opportunities for the company.
Urška Sršen and Sando Mur founded Bellabeat, a high-tech company that manufactures health-focused smart products.I am a junior data analyst working on the marketing analyst team at **Bellabeat**. Sršen knows that an analysis of Bellabeat’s available consumer data would reveal more opportunities for growth. She has asked the marketing analytics team to focus on a Bellabeat product and analyze smart device usage data in order to gain insight into how people are already using their smart devices. Then, using this information, she would like high-level
recommendations for how these trends can inform Bellabeat marketing strategy.

**Stakeholders:**

**Primary Stakeholders:**
 Urška Sršen: Bellabeat’s cofounder and Chief Creative Officer.
 Sando Mur: Mathematician and Bellabeat’s cofounder; key member of the Bellabeat executive team.
 
 **Secondary Stakeholders:**
 Bellabeat marketing analytics team: A team of data analysts responsible for collecting, analyzing, and
reporting data that helps guide Bellabeat’s marketing strategy.

## Buisness Task
Analyze smart device usage data in order to gain insight into how consumers use non-Bellabeat smart
devices. And then select one Bellabeat product to apply these insights to in our presentation.

#### Preparing Data for Analysis 

Data Sources Used:

  * The dataset used for this analysis is: [Link](FitBit Fitness Tracker Data)

  * License: (CC0:PublicDomain)

  * Dataset made available through Mobius

This Kaggle dataset contains personal fitness tracker from thirty fitbit users. Thirty eligible Fitbit users consented to the submission of personal tracker data, including minute-level output for physical activity,heart rate,and sleep monitoring. It includes information about daily activity, steps, and heart rate that can be used to explore users’ habits.

## Data exploration

### 1.Load packages


```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}

library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidyr)
library(skimr)
library(janitor)
```
### 2. Import datasets


```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
dailyActivity <- read_csv("C:/Users/deeps/Desktop/Bellabeat_CaseStudy/dailyActivity_merged.csv")
dailyCalories <- read_csv("C:/Users/deeps/Desktop/Bellabeat_CaseStudy/dailyCalories_merged.csv")
dailyIntensities <- read_csv("C:/Users/deeps/Desktop/Bellabeat_CaseStudy/dailyIntensities_merged.csv")
hourlyIntensities <- read_csv("C:/Users/deeps/Desktop/Bellabeat_CaseStudy/hourlyIntensities_merged (1).csv")
sleepDay <- read_csv("C:/Users/deeps/Desktop/Bellabeat_CaseStudy/sleepDay_merged.csv")
weightLogInfo <- read_csv("C:/Users/deeps/Desktop/Bellabeat_CaseStudy/weightLogInfo_merged.csv")

```
### 3. Inspecting the datasets


```{r
# Inspecting the following datasets:

# Datasets : dailyActivity, dailyCalories, dailyIntensities, hourlyIntensities, sleepDay, weightLogInfo}

colnames(dailyActivity)
colnames(dailyCalories)
colnames(dailyIntensities)
colnames(hourlyIntensities)
colnames(sleepDay)
colnames(weightLogInfo)

```


Summarize or preview the datasets with the `glimpse()` and skimr() functions to get a better understanding of the data by running the code chunks below:


```{r}
glimpse(dailyActivity)
glimpse(dailyCalories)
glimpse(dailyIntensities)
glimpse(hourlyIntensities)
glimpse(sleepDay)
glimpse(weightLogInfo)
```

```{r}
skim_without_charts(dailyActivity)
skim_without_charts(dailyCalories)
skim_without_charts(dailyIntensities)
skim_without_charts(hourlyIntensities)
skim_without_charts(sleepDay)
skim_without_charts(weightLogInfo)
```

```{r}
head(dailyActivity)
head(dailyCalories)
head(dailyIntensities)
head(hourlyIntensities)
head(sleepDay)
head(weightLogInfo)
```

```{r}
# Inspecting the distinct Id's in the six data frames:
n_distinct(dailyActivity$Id)
n_distinct(dailyCalories$Id)
n_distinct(dailyIntensities$Id)
n_distinct(hourlyIntensities$Id)
n_distinct(sleepDay$Id)
n_distinct(weightLogInfo$Id)
```

## Result of the above inspection:

1. 


 


